\documentclass[12pt, letterpaper]{article}

\begin{document}
\centerline{\begin{tabular}{*3{c}}
	\parbox[t]{0.7\linewidth}{\begin{center}{\textbf{Cinnamon Rolls}}\\\end{center}}
	\end{tabular}}
\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Dough Ingredients:}\bigbreak
\normalsize
1.\hspace{0.3cm}  $\frac{1}{2}$ cup scalded milk
\smallbreak
2.\hspace{0.3cm}  $1\frac{1}{4}$ cup sugar
\smallbreak
3.\hspace{0.3cm}  $1$ egg
\smallbreak
4.\hspace{0.3cm} $1$ teaspoon salt
\smallbreak
5.\hspace{0.3cm}  $\frac{1}{3}$ cup butter or shortening
\smallbreak
6.\hspace{0.3cm} $3\frac{1}{2}–4$ cups All Purpose flour.
\smallbreak
7.\hspace{0.3cm}  $\frac{1}{2}$ cup warm water
\smallbreak
8.\hspace{0.3cm}  $\frac{1}{4}$ ounce Packet yeast

\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Dough Preparation:}\bigbreak
\normalsize

1.\hspace{0.3cm}In a small bowl add: \smallbreak
\hspace{0.6cm}yeast\smallbreak
\hspace{0.6cm}$\frac{1}{2}$ cup warm water\smallbreak
\bigbreak

2.\hspace{0.3cm}In a large bowl combine: \smallbreak
\hspace{0.6cm}$1\frac{1}{4}$ cup sugar\smallbreak
\hspace{0.6cm}$\frac{1}{3}$ cup melted butter\smallbreak
\hspace{0.6cm}$1$ teaspoon salt\smallbreak
\hspace{0.6cm}1 egg\smallbreak
\hspace{0.6cm}2 cups flour\smallbreak

3.\hspace{0.3cm}Mix until smooth

4.\hspace{0.3cm}Add Yeast and Water

4.\hspace{0.3cm}Mix in remaining $1\frac{1}{2}-2$ cups flour until dough is easy to handle

5.\hspace{0.3cm}Knead dough on lightly floured surface for 5 to 10 minutes.

6.\hspace{0.3cm}Place in well-greased bowl, cover and let rise until doubled in size, 
\smallbreak
\hspace{0.6cm}$1-1\frac{1}{2}$ hours.

\break 
\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Filling Ingredients:}\bigbreak
\normalsize
1.\hspace{0.3cm}  $\frac{1}{2}+$ cup melted butter
\smallbreak
2.\hspace{0.3cm}  $\frac{3}{4}+$ cup sugar
\smallbreak
3.\hspace{0.3cm}  $2$ tablespoons ground cinnamon
\smallbreak
4.\hspace{0.3cm} $\frac{3}{4}$ cup walnut or pecans, \textit{optional}
\smallbreak


\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Filling Preparation:}\bigbreak
\normalsize
1.\hspace{0.3cm}Mix sugar and cinnamon.

2.\hspace{0.3cm}Melt butter in a separate container.

3.\hspace{0.3cm}Remove risen dough and make into a 15"x9" rectangle.

4.\hspace{0.3cm}Spread melted butter over upper side of dough.

4.\hspace{0.3cm}Sprinkle sugar and cinnamon over dough.

5.\hspace{0.3cm}Sprinkle on any other toppings.

6.\hspace{0.3cm}Grab the 15" side of the dough and roll up the dough and pinch the 
\smallbreak
\hspace{0.6cm}edges to seal in butter mixture.

7.\hspace{0.3cm}Cut the roll into $12-15$ slices.

8.\hspace{0.3cm}Cover a baking pan with melted butter.

9.\hspace{0.3cm}Sprinkle sugar over the butter.

10.\hspace{0.1cm}Place cinnamon roll slices on pan and allow to rise for about 45 
\smallbreak
\hspace{0.6cm}minutes.

\break
\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Baking Instructions:}\bigbreak
\normalsize
1.\hspace{0.3cm}Preheat oven to 350$^\circ$F

2.\hspace{0.3cm}After dough has risen bake for  $\leq30$ minutes.


\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Glaze Ingredients:}\bigbreak
\normalsize
1.\hspace{0.3cm}  $4$ tablespoons butter
\smallbreak
2.\hspace{0.3cm}  $2$ cups powdered sugar
\smallbreak
3.\hspace{0.3cm}  $1$ tablespoons vanilla extract
\smallbreak
4.\hspace{0.3cm} $3-6$ tablespoons \textit{hot} water
\smallbreak
\begin{center}\noindent\rule{15cm}{0.4pt}\end{center}
\large{Glaze Instructions:}\bigbreak
\normalsize
1.\hspace{0.3cm}In a measuring cup add: \smallbreak
\hspace{0.6cm}butter\smallbreak
\hspace{0.6cm}vanilla extract\smallbreak
\hspace{0.6cm}powdered sugar\smallbreak
\smallbreak

2.\hspace{0.3cm}Add 1 tablespoon of water at a time until glaze reaches desired 

\hspace{0.6cm}consistency.
\smallbreak
3.\hspace{0.3cm}Pour glaze over rolls after finished baking.

\end{document}